Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-09-22 paper.qmd
Changed to render autjor best model PBMC

axes_obj <- gen_axes(
  proj = projection,
  limits = 1.5,
  axis_pos_x = -0.75,
  axis_pos_y = -0.75,
  axis_labels = names(scaled_pbmc_data),
  threshold = 0.07)

>>>>

axes_obj <- gen_axes(
  proj = projection,
  limits = 1.5,
  axis_pos_x = -0.75,
  axis_pos_y = -0.75,
  axis_labels = names(scaled_pbmc_data),
  threshold = 0.084)
